---
title: "Language Survey responses visualisation"
author: "Ben Liu"
date: "27 April 2015"
output:
  word_document: default
  pdf_document:
    highlight:
    - zenburn
    toc:
    - yes
  html_document:
    theme:
    - united
    toc:
    - yes
---

## Introduction

Questionnaire can be found in this link (Google Form): <https://docs.google.com/a/maqleurope.com/forms/d/1LDAchdyIxuEQpq8oscPU8RAmI-F2hfop43tSmC7OpLc/edit?usp=drive_web>.

Responses are gathered in a Google Sheet *(require Marvelous login to open)* <https://docs.google.com/a/maqleurope.com/spreadsheets/d/1qd2kq2ZmoHb1uv61DrWudpqwKCVQmd6ORj5zwMnWQ-A/edit#gid=916513353>.

This R script will parse real-time responses from Google Sheet, then visualise the results. 

```{r,cache=T,echo=F,warning=F,cache.comments=F,message=F,error=F,background=F}
# setwd("~/Google Drive/R working/twitteR/")
# setwd("C:/Users/Ben/Google Drive/R working/twitteR/")
# setwd("C:/Users/Harry Samsung Laptop/Desktop/")
source("lang survey.r")
```


## Summary

In total, `r nrow(raw)` participants from `r length(unique(raw$country))` countries, speaking `r length(unique(raw$language))` languages, have responded the survey. 


### Respondents' resident countries and primary languages

Answers for the first two questions are combined for comparison. 

```{r,echo=F,cache=F,warning=F,comment=F,message=F,fig.width=8}
require(dplyr)
require(ggplot2)
require(gridExtra)

# plot countries
df=raw %>% 
    group_by(country) %>%
    summarise(count=n()) %>%
    arrange(desc(count)) %>%
    filter(count>=5)
# shorten country names
df$country=gsub("United Kingdom of Great Britain and Northern Ireland","UK",df$country)
df$country=gsub("United States of America","USA",df$country)

df$country=factor(df$country,levels=arrange(df,count)$country)

p1=ggplot(df,aes(x=country,y=count))+coord_flip()+geom_bar(stat="identity")+labs(x="Countries",y="Number of respondents",title="Country of residence")

# plot language
df=raw %>% 
    group_by(language) %>%
    summarise(count=n()) %>%
    arrange(desc(count)) %>%
    filter(count>=5)

df$language=factor(df$language,levels=arrange(df,count)$language)

p2=ggplot(df,aes(x=language,y=count))+coord_flip()+geom_bar(stat="identity")+labs(x="Languages",y="Number of respondents",title="Primary language")

# create a frame for comparison
grid.arrange(p1,p2,ncol=2)

```

### Japanese games fan

```{r,echo=F,cache=T,cache.comments=F,warning=F}
require(dplyr)
df=as.data.frame(table(raw$japan_game_fan))
```

`r round(df[df[,1] %in% "Varies",2]/sum(df[,2])*100,digits = 0)`% of respondents are still confused whether they like Japanese games or not.

Within `r df[df[,1] %in% "Yes",2]` respondents who claimed to be Japanese games fans, `r round(nrow(raw[!(raw$purchased_game %in% "I've never purchased a Marvelous Europe game"),])/df[df[,1] %in% "Yes",2]*100,digits=0)`% have purchased one or more Marvelous games.


```{r,echo=F,cache=T}
# Q3 are you japanese game fan
qplot(raw$japan_game_fan,
      main="Are you a Japanese games fan?",
      xlab="Number of respondents")
```

### Purchased Marvelous games

```{r,cache=T,echo=F}
# Q4 purchased game before
# breakdown multiple answers
purchased_game=unlist(strsplit(raw$purchased_game,", "))
df=data.frame(purchased_game,rep(1,length(purchased_game)))
names(df)=c("game","count")
df=df %>%
  group_by(game) %>%
  summarise(total=sum(count)) %>%
  arrange(desc(total))
df$game=factor(df$game,levels=arrange(df,total)$game)
```

`r round(df[df$game %in% "SENRAN KAGURA: Burst",]$total/nrow(raw)*100,digits=0)`% of the respondents have purchased Senran Kagura Burst before. Shinovi Versus is catching up with `r round(df[df$game %in% "SENRAN KAGURA: Shinovi Versus",]$total/nrow(raw)*100,digits=0)`%, despite Shinovi Versus was only released digitally in Europe.

With hindsight, Rune Factory 4, possessed by `r round(df[df$game %in% "Rune Factory 4",]$total/nrow(raw)*100,digits=0)`% of respondents, could have achieved better sales if we release physical edition in Europe. 

`r round(nrow(raw[raw$purchased_game %in% "I've never purchased a Marvelous Europe game",])/nrow(raw)*100,digits=0)`% of respondents haven't purchased any Marvelous games before. We certainly want to convert this percentage into our sales growth. 


```{r,echo=F,cache=T}
ggplot(df,aes(x=game,y=total))+coord_flip()+geom_bar(stat="identity")+labs(x="Game",y="Purchases",title="Marvelous games purchased")
```

### Choice of language in games

`r round(nrow(raw[raw$lang_choice %in% "Yes",])/nrow(raw)*100,digits=0)`% ask for a choice of language options.

```{r,echo=F}
# 5. Would you prefer games to offer a choice of language options?	
qplot(raw$lang_choice,
      main="Prefer games with a choice of language options",
      xlab="Number of respondents")
```


### Buy games in primary language

`r round(nrow(raw[!(raw$buy_if_primary_lang %in% "No") & raw$purchased_game %in% "I've never purchased a Marvelous Europe game",])/nrow(raw)*100,digits=0)`% of respondents who haven't bought Marvelous games would at least think about buying if the game is localised in their primary languages.

```{r,echo=F}
# 6. Would you be more likely to buy a game if it was in your primary language?	
qplot(raw$buy_if_primary_lang,
      main="Prefer games with a choice of language options",
      xlab="Number of respondents")
```


### Localisation - audio dub or subtitle
```{r,echo=F}
# 7. Do you prefer audio dub or subtitle localisation?	
qplot(raw$dub_or_sub,
      main="Audio dub or subtitle localisation",
      xlab="Number of respondents")
```


### Dual audio in both Japanese and local language
```{r,echo=F}
# 8. Is offering dual audio (Both Local and Japanese) important to you?
qplot(raw$dual_audio,
      main="Importance of offering dual audio",
      xlab="Number of respondents")
```


### Survey entries per country 

This chart is for Mike.

```{r,echo=F,warning=F,cache.comments=F,cache=F,fig.width=8,error=F}
# convert timestamp
library(scales)
raw$timestamp=as.POSIXlt(raw$timestamp,format="%d/%m/%Y %H:%M:%S")

raw$country=gsub("United Kingdom of Great Britain and Northern Ireland","UK",raw$country)
raw$country=gsub("United States of America","USA",raw$country)

qplot(timestamp, country, data=raw, geom="point")+scale_x_datetime(breaks=date_breaks("1 day"),minor_breaks = "1 hour")
```
